%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Gustavo Puglia} \\[7.5pt]
\href{https://github.com/gpuglia}{\raisebox{-0.05\height}\faGithub\ gpuglia} \ $|$ \ 
\href{https://linkedin.com/in/gustavopuglia}{\raisebox{-0.05\height}\faLinkedin\ gustavopuglia} \ $|$ \ 
\href{mailto:gpugliac@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ gpugliac@gmail.com} \ $|$ \ 
\href{tel:+584143264428}{\raisebox{-0.05\height}\faMobile \ +58.414.326.4428} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Senior Software Engineer with 8+ years of experience working primarily with Ruby-on-Rails across both greenfield and legacy applications. Particularly enjoys collaborating with Product teams and Business stakeholders to understand user needs, and to provide insight into technical possibilities. Has both led team projects, as well as executed solo initiatives.

\section{Skills}
Ruby, Ruby-on-Rails, Kotlin, Spring Boot, PostgreSQL, JavaScript, EmberJs, ReactJS

%Experience
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Stripe - API Engineer} & \hfill Jan 2021 - present \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Launched Stripe in the United Arab Emirates as part of the EMEA Expansion team. After a succesful launch, transitioned to the EMEA Growth team to increase customer acquisition and conversion rates.}  \\ \\
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Owned and executed on a complete refactor of our Continuous Verification system, a key module in our identity verification system. Resulted in substantial technical and commercial wins, improving reliability, reducing KTLO burden and simplyfing the codebase, whilst also leading to a 15\% increase in resubmission of expired identity documents.
        \item[--] Led an experimental project, involving significant A/B testing, to increase application completion rates by redesigning our global onboarding email flow. Resulted in an increase of 0.55\% in conversion rates, which is equivalent to \$5M of yearly net revenue.
        \item[--] Enabled self-service sign-ups in the UAE, allowing users to register onto Stripe without human intervention – a first-in-class for the region. As a result, the payments volume in the country doubled, all while maintining our target of 80\% of application submitted and reviewed in under 24 hours.
        \item[--] Transformed the UAE sign-up experience from a disjointed series of steps, recycled from our onboarding flow in other countries, into a unified, harmonious flow as part of Stripe's launch in the UAE.
    \end{itemize}
    \end{minipage}
}
\end{tabularx}


\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{AlphaSights - Senior Software Enginer} & \hfill Jun 2019 - Jan 2021 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Technical lead for a team of 5 full-stack engineers responsible for the long-term tech strategy for the products under the Client Protection remit.}  \\ \\
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Architected and developed an Entity Resolution (ER) solution for a database of 7M+ company records. Achieved this by enriching core company records by integrating and leveraging a number of third-party datasets. Evolved the ER algorithm's match rate from a base of 15\% to 75\% over three months.
        \item[--] Automated the detection of publicly traded companies in an expert's career history. Built a rule engine that determines whether a company is public or private, based on available financial and legal data. Built a Change Data Capture engine that keeps a company's status up to date by reacting to changes in the available data. Reduced task completion time by 80\%. 
        \item[--] Centralised all risk monitoring by consolidating five different tools into a single platform. This tool is now regarded as the single source of truth by the internal Compliance and Legal business unit.
        \item[--] Developed an internal tool to allow associates to conduct background checks on over 100k advisors per year. Worked closely with a small group of end users to incorporate this step into their workflow with minimal disruption.
    \end{itemize}
    \end{minipage}
}
\end{tabularx}


\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{AlphaSights - Software Enginer} & \hfill Sep 2014 - Jun 2019 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Worked with a team of 4 engineers, which I then proceeded to lead. Mentored 2 new engineers through our graduate program.}  \\ \\
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Took ownership of the proprietary Finance and Transaction system; maintaining them for over 5 years. Refactored the entire codebase to provide robustness and auditability. Leveraged this refactor to extend the system on multiple occasions including supporting wholesale changes in our pricing and performance pay engines.
        \item[--] Implemented a mass payouts system that supports over £25M of volume annually to more than 80 countries. Integrated with multiple payment providers, and bult a routing layer to select the optimal one based on price, speed, and quality.
    \end{itemize}
    \end{minipage}
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Project Enginer - Grupo CorpData} & \hfill Mar 2019 - Jan 2021 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Led a team of 4 engineers in the design of a data centre and internal network for a new Bolivariana de Puertos S.A site – the Venezuelan government agency responsible for port management.
        \item[--] Directed the implementation of a video wall and monitoring solution for the Venezuelan government Emergency Response Service.
    \end{itemize}
    \end{minipage}
}
\end{tabularx}
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2006 - 2012 & Telecommunications Engineer at \textbf{Universidad Católica Andrés Bello} \\

\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
